Reasoning Graphically about Quantum Computation

### 2008-02-23 papers/reasoning-graphically/paper.tex
added secions and edited the abstract
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1349 f8f375fb-4f10-0410-8d47-b6fbdc7ca053

\begin{abstract}
  Systems of quantum computation are typically represented by large
  matrix compositions. However, recent graph-based formalisms offer an
  approach which exposes the structure of these systems in a clearer
  and more accessible way. Although these provide significantly
  simpler way of reading and presenting quantum computations, manual
  manipulation of such graphs is slow, arduous, and error prone. We
  present a formalism that supports a mechanised reasoning about such
  graphs. This involves a compositional account of graph rewriting
  that meets the underlying categorical semantics for the model of
  quantum computation. In particular, we present system, which has
  been implemented, with a fixed logical kernel and which gives a
  declarative account and supports derived rules. Soundness of the
  system is proved with respect to the underlying model of quantum
  computation and completeness is an open problem.

@@

\section{Introduction}

blah blah

\bibliographystyle{plain}
\bibliography{bibfile}

>>>>

\begin{abstract}
  Systems of quantum computation are typically represented by large
  matrix compositions. However, recent graph-based formalisms offer an
  approach which exposes the structure of these systems in a clearer
  and more accessible way. Although these provide a significantly
  simpler way of reading and presenting quantum computations, manual
  manipulation of such graphs is slow and error prone. We
  present a formalism that supports a mechanised reasoning about such
  graphs. This involves a compositional account of graph rewriting
  that preserves the underlying categorical semantics. We present a
  system, which has been implemented, with a fixed logical kernel and
  support for derived rules, which allows the model of quantum
  computation  to be specified declarativley.
  Soundness of the 
  system is proved with respect to the underlying model and
  completeness is an open problem.

@@

\section{Introduction}
\label{sec:introduction}

\section{Compact Categories and Graphs}
\label{sec:mono-categ-graphs}

\section{Representation and Compositionality}
\label{sec:repr-comp}

\section{Graph Patterns and Matching}
\label{sec:graph-patt-match}

\section{Conclusions}
\label{sec:conclusions}

Ideas for further work
\begin{itemize}
\item simplification ordering
\item confluence arguments for graphs
\item formalise algorithms in a thm prover
\item richer graph structures - quantification over edges
\item richer expression language in vertices
\item completeness of rewrite rules with respect to wpHilb
\end{itemize}

\bibliographystyle{plain}
\bibliography{all}
\bibliography{bibfile}
